Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-03 article-models-ttderived.tex
added remark about diagrams of type theory

>>>>

Because composition is proven to be associative, we can draw diagrams involving
families and morphisms between them in a context $\Gamma$, just as is usual in
category theory and the order in which the morphisms are composed has no
relevance. We can also speak about pullback diagrams, with universality in a
judgmental sense.
